Stable Neo-Hookean Flesh Simulation

### 2019-10-07 LaTeX-Master-Vorlage/chapter/Background.tex
working mostly on background

\chapter{Background} \label{c:Background}
The goal we are striving for is to simulate human-like characters. In order to narrow it down even further we concentrate on the behaviour of the flesh of the character. 
For understanding the thematics of simulating human-like flesh it is necessary to have a basic mathematical background and knowledge of continuum mechanics. The goal of this chapter is to deliver an understanding in the topics mentioned.

In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation}. The goal of the paper was to model deformations for virtual characters that have human-like features.

\section{Notation and Convention}
At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics taken from \cite{Spencer1980}. Additionally we will include the declarations formulated in the paper \textit{Stable Neo-Hookean Flesh Simulation}.

@@

@@

In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{.}$ as shown above.

Additionally we will have to deal with $4^{th}$ order tensors in the following form of matrix-of-matrices:

@@

These matrices are denoted by using blackboard bold.
\\
If we now vectorize $\mathbb{A}$ we receive the following form:

@@

This term is equivalent to the following notation:

@@

The advantage of this form is that we can write several expressions as a cross product which we will need later.

\subsection{Summary}
A quick overview of the used notation:

\begin{addmargin}[2cm]{2cm}
a: scalar \\
\textbf{A}: matrix or tensor \\
\textbf{a}: vector \\
vec(\textbf{A}) = $\boldsymbol{\check{a}}$: vectorized matrix
\end{addmargin}

\section{Mathematical Background}

Since mathematics plays an important role in our field of interest we will build a solid background in this chapter. A basic understanding of linear algebra is assumed.

@@

\section{Continuum Mechanics}
In this section we will give a broad introduction the field of Continuum Mechanics.
In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but concentrate on pieces of matter which are in comparison very large. We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p. 1).

\section{Deformation}
Graphically we can imagine a deformation with the help of a deformation map. In Fig. \ref{fig:deformationmap} we have on the left side an ellipse that signifies an object in its rest state. On the right side in the same image we can see the ellipse in a deformed state. We can map each point from its rest state to the deformed one with the help of the function $\phi$.

@@

When applying a force over an object naturally the object itself undergoes a deformation. In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area.

>>>>

\chapter{Background} \label{c:Background}
The goal we are striving for is to animate human-like characters. In order to narrow it down even further we concentrate on the behaviour of the flesh of the character. 
For understanding the thematics of simulating human-like flesh it is necessary to have a basic mathematical background and knowledge of continuum mechanics. The goal of this chapter is to deliver an understanding in the topics mentioned.

\section{Notation and Convention}
At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics taken from the book \textit{Continuum Mechanics} \cite{Spencer1980}. Additionally we will include some more specific declarations formulated in the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.

@@

In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{.}$ as shown in the following equation:

@@

Additionally we will have to deal with $4^{th}$ order tensors in a form of matrix-of-matrices. These matrices are denoted by using blackboard bold:

@@

If we now vectorize $\mathbb{A}$ we receive the form described in the following:

@@

This term above is equivalent to the following notation:

@@

The advantage of this form is that we can write several expressions as a cross product. We will need this property later to simplify complicated expressions and calculations.

\subsection{Summary}
A quick overview of the notation used so far:

\begin{addmargin}[1cm]{1cm}
a: Scalar \\
\textbf{A}: Matrix or tensor \\
\textbf{a}: Vector \\
vec(\textbf{A}) = $\boldsymbol{\check{a}}$: Vectorized matrix
\end{addmargin}

\section{Mathematical Background}
Since mathematics play an important role in our field of interest we need to build a solid background before we go further into the physics part. This chapter should cover all the important concepts used later in the calculations. A basic understanding of linear algebra is assumed.

@@

\todoredefined[inline]{
TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end.
}

\section{Continuum Mechanics}
In this section we will give a broad introduction into the field of Continuum Mechanics. In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but rather concentrate on pieces of matter which are in comparison very large. We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p. 1).

\section{Deformation}
When applying a force over an object naturally the object itself undergoes a deformation. In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area.

\todoredefined[inline]{
TODO: Decide whether to include the above paragraph and how to connect it better to the paper.
}

Now let us have a look at a deformation in a rather mathematical sense. Graphically we can imagine a deformation with the help of a two dimensional deformation map as shown in Fig. \ref{fig:deformationmap}. Here we have on the left side an ellipse that represents an object or material in its rest state. A function $\phi$ maps this rest state of the ellipse to a deformed state shown in Fig. \ref{fig:deformationmap} on the right side. Mathematically spoken this means that we can map each point of a chosen object from its rest state to a deformed one.

@@

In conclusion the function $\phi$ describes our deformation. If we derive $\phi$ we can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense:

\[
\begin{array}{l}
{\text { Deformation gradient: }} {\mathbf{F}=\operatorname{\nabla} \phi}
\\
{\text { Length changes: }} {\qquad I_{C}=\operatorname{tr}\left(\mathbf{F}^{T} \mathbf{F}\right)} 
\\ 
{\text { Volume changes: }} {\qquad J=\operatorname{det}(\mathbf{F})}\end{array}
\]

\todoredefined[inline]{
TODO: Adjust so the equal sign is at the same place in each column.
}

### 2019-10-07 LaTeX-Master-Vorlage/chapter/Introduction.tex
working mostly on background

\chapter{Introduction}
\textit{"Animation offers a medium of story telling and visual entertainment which can bring pleasure and information to people of all ages everywhere in the world."} \\
- Walt Disney

@@

In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} the authors addressed exactly the problem of making an animated movement of a human-like character look as natural as possible. In order to animate a physical movement we need to understand the physics behind it which lies in the field of continuum mechanics. Unfortunately most of the time it has yet to be learned. The goal of this thesis is for a regular computer science student to give the necessary physical and mathematical background to understand the field of animation and maybe make a contribution to the field.

>>>>

\chapter{Introduction}
\textit{``Animation offers a medium of story telling and visual entertainment which can bring pleasure and information to people of all ages everywhere in the world.``} \\
- Walt Disney

@@

In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} the authors addressed exactly the problem of making an animated movement of a human-like character look as natural as possible. In order to animate a physical movement we first need to understand the physics behind it which lies in the field of continuum mechanics. Unfortunately for most of us it has yet to be learned. The goal of this thesis is for a regular computer science student to give the necessary physical and mathematical background to understand the field of animation and maybe make a contribution to the field.
